### 2014-07-25 ApTranscriptome_TR.Rmd
updates

**June 16, 2014**

@@

```{r gsea_Ar_int_A22_low_cluster}
# similarity among enriched GO terms
Ar.int.A22.low.gsea.term.sim <- termSim(Ar.int.A22.low.gsea$GO.ID, Ar.int.A22.low.gsea$GO.ID, ont = "BP", organism = 'fly')
# replace GO IDs with terms
rownames(Ar.int.A22.low.gsea.term.sim) <- Ar.int.A22.low.gsea$Term
colnames(Ar.int.A22.low.gsea.term.sim) <- Ar.int.A22.low.gsea$Term
# distance matrix
Ar.int.A22.low.gsea.term.sim.hclust <- hclust(dist(Ar.int.A22.low.gsea.term.sim))
plot(Ar.int.A22.low.gsea.term.sim.hclust)
# report items in each cluster at height 1.8
(Ar.int.A22.low.hclust.report <- GSEAReportClusters(Ar.int.A22.low.gsea.term.sim.hclust, h = 1.6))
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, qlslope, qlmean, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.varint, t.varbim, T_on.high.ttest, T_on.low.ttest, Ap.gsea.intersect, Ap.gsea.union, file = "ms.RData")
```

>>>>

**July 17, 2014**

@@

```{r gsea_Ar_int_A22_low_cluster}
# similarity among enriched GO terms
Ar.int.A22.low.gsea.term.sim <- termSim(Ar.int.A22.low.gsea$GO.ID, Ar.int.A22.low.gsea$GO.ID, ont = "BP", organism = 'fly')
# replace GO IDs with terms
rownames(Ar.int.A22.low.gsea.term.sim) <- Ar.int.A22.low.gsea$Term
colnames(Ar.int.A22.low.gsea.term.sim) <- Ar.int.A22.low.gsea$Term
# distance matrix
Ar.int.A22.low.gsea.term.sim.hclust <- hclust(dist(Ar.int.A22.low.gsea.term.sim))
plot(Ar.int.A22.low.gsea.term.sim.hclust)
# report items in each cluster at height 1
(Ar.int.A22.low.hclust.report <- GSEAReportClusters(Ar.int.A22.low.gsea.term.sim.hclust, h = 1.2))
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, qlslope, qlmean, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.varint, t.varbim, T_on.high.ttest, T_on.low.ttest, Ap.gsea.intersect, Ap.gsea.union, Ar.int.A22.bim.gsea, Ar.int.A22.low.gsea, file = "ms.RData")
```
